% LaTeX resume using res.cls
\documentclass[line,margin]{res}
\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{P\textsc{atrick} A\textsc{nthony} J\textsc{ohnson}}
\address{256 Stoney Cliff rd. Centerville, MA 02632}
\address{p.johnson125@gmail.com}
\address{(508) 776-7664}
 
\begin{resume}
 
\section{SUMMARY} Dedicated professional with strong analytical and organizational skills. Exceptional written and verbal communication. Advanced technical aptitude; implementing and maintaining a variety of systems and technologies. Reliable. Exceptional problem solving skills. Easily adabptable; friendly easy going with fantastic customer service. \\ 

 
\section{COMPUTER \\ SKILLS}
                {\sl Languages \& Software:}
                    \begin{itemize} \itemsep -2pt
                        \item   Ruby, Python, Rails, HTML, CSS, Coldfusion.
                        \item   Git.
                        \item  Documentation tools including \LaTeX.
                    \end{itemize}

                {\sl Operating Systems:}
                     \begin{itemize} \itemsep -2pt 
                        \item   Windows (XP - 8).
                        \item   Linux (Debian, Ubuntu, centOS).
                     \end{itemize}

                {\sl Miscellaneous Skills:}
                    \begin{itemize} \itemsep -2pt
                      \item   PC repair, Troubleshooting \& support.
                      \item   Installation of operating systems.
                    \end{itemize}
 
\section{EXPERIENCE} {\sl Contact Manager} \hfill 2012-2013 \\
                The Vista Companies Cotuit MA
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                  \item   Remodeled contact management system and mailing lists.
                   
                  \end{itemize}
 

                {\sl Mobile Equipment Repair} \hfill 2009-2011 \\
                Chuck Mayo, Marston Mills, MA
                  \begin{itemize}
                  \item Parts Delivery
                  \item Mechanic
                  \end{itemize}  
                  
                   {\sl Flood Analyst/Project Coordinator } \hfill 2007 - 2009 \\
                First Track Information Services
                  \begin{itemize}  \itemsep -2pt %reduce space between items
                  \item  Database Administrator
                  \item  Flood plain analyst
                  \end{itemize} 

\section{EDUCATION} {\sl Cape Cod Community College} \\
                Barnstable, MA 
                2004 through 2006 \\
                Concentration: Business

                {\sl Massachusetts Institute of Technology } \\
                2011-2012 \\
                Computer Science 600.0x Certification\\
 

\end{resume}
\end{document}
